Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2017-03-01 websci-2017/source/paper.tex
Update discussion conclusion abstract.

\maketitle
\begin{abstract}
Networks with single points of failure are particularly susceptible to
targeted attacks.
In communication networks, these types of faults can leave users vulnerable to
censorship and targeted surveillance,
even when cryptography is utilized.
Centralized networks have single points of failure by definition,
leading to a growing popularity in decentralized architectures and protocols.
However, centralized network structure can arise even when protocols are
decentralized.
Despite being based on decentralized protocols,
the Internet and World-Wide Web have
been shown both theoretically and historically to be highly susceptible to
adversarial faults, in part due to emergent structural centralization.
Existing network trust models, such as webs of trust, fail to adequately address
network structure.
We describe a novel, adversarial fault-tolerant,
concurrent multipath routing algorithm for the decentralized
butterfly network topology.
We also develop a partial trust model that makes it possible to
quantify the adversarial fault tolerance of a network,
and which makes more realistic transitivity assumptions than webs of trust.
When network topology can be dictated, these results can be used to create
scalable, attack-tolerant infrastructures. More generally, our results provide
a formalism for evaluating the effects of network structure on adversarial
fault tolerance.
\end{abstract}

@@

\vskip 3em

@@

While decentralized protocols have received much attention for their potential
fault tolerance applications,
a better understanding of how network structure contributes to fault tolerance
is necessary.
We have proposed a network-based scheme for adversarial fault tolerance on the
butterfly topology,
utilizing a novel {\em concurrent multipath routing} algorithm.
We have also demonstrated how {\em partial trust transitivity},
in addition to being more realistic than infinite transitivity,
enables the analysis of the relationship between trust, network structure,
and fault tolerance.

@@

We have focused specifically on adversarial faults that block or
change messages (e.g., censorship).
We have not specifically addressed {\em confidentiality}:
how to keep those messages private.
Existing cryptographic techniques for confidentiality are relatively
mature compared to those for tolerating censorship.
In fact, an attacker might use targeted attacks to achieve censorship
as a fallback when surveillance isn't feasible.
However, the techniques presented in this paper
are entirely compatible with, and in some cases could enhance, existing
confidentiality techniques.
For example, {\em man-in-the-middle} attacks exploit a privileged
network position to attack otherwise secure cryptography,
suggesting that structural approaches can complement cryptographic ones.

While our present proposal is specific to the butterfly topology,
the multipath fault tolerance scheme could
be applied to any network that has both sufficient redundancy and a
routing algorithm to discover independent paths.
For general networks, finding all such paths is NP-hard,
but efficient, suboptimal algorithms exist
\cite{reiter_resilient_1998}.
However, our approach is best suited for structured networks.
While the ability to control network topology is only achievable in some
applications, those applications are nonetheless significant
(e.g. overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}).
Furthermore, when high levels of adversarial fault tolerance are required,
designers of new sociotechnical systems might choose to
incorporate such networks.
For example,
a coalition of groups supporting free expression could use our results
to construct a censorship-resistant communication network
by cultivating the necessary trust relationships.

@@

We have presented a novel multipath routing algorithm for the butterfly
topology,
as well as a scheme for using this algorithm to achieve a high level of
attack-tolerance in a communication network,
even when no single path is entirely trusted.
Under this scheme, the probability of an adversary causing an undetectable error
decreases exponentially with the network's effective redundancy.
The effective redundancy, in the case of the butterfly topology,
grows exponentially with the trust radius.
Furthermore, a small increase in the number of messages sent can compensate
for a large increase in the number of messages compromised by an adversary.
We have also demonstrated how the assumption of partial trust
transitivity can enable a formal analysis of the effects of network structure
on attack-tolerance.
These results are directly applicable to systems in which the link
structure can be imposed by the designer,
and more generally, provide a formalism that can be used more to evaluate
the role of network structure, trust transitivity, and effective redundancy
on adversarial fault tolerance.

>>>>

\maketitle
\begin{abstract}
Targeted attacks against network infrastructure are notoriously difficult
to withstand.
Much of the existing work on network fault-tolerance focuses on random faults and
does not apply to adversarial faults (attacks).
In the case of communication networks,
targeted attacks can leave users vulnerable to
censorship and targeted surveillance,
even when cryptography is used.
Centralized networks have single points of failure by definition,
leading to a growing popularity in decentralized architectures and protocols
for greater fault-tolerance.
However, centralized network {\em structure} can arise even when {\em protocols} are
decentralized.
Despite their decentralized protocols,
the Internet and World-Wide Web have
been shown both theoretically and historically to be highly susceptible to
attack, in part due to emergent structural centralization.
When single points of failure exist,
they are potentially vulnerable to non-technological
(i.e., coercive) attacks,
suggesting the importance of a structural approach to attack-tolerance.
We show how the assumption of partial trust transitivity,
while more realistic than the assumption used by webs of trust,
can be used to quantify the effective redundancy of a network
as a function of trust transitivity.
We also prove that the effective redundancy of the wrap-around butterfly topology
increases exponentially with trust transitivity and
describe a novel concurrent multipath routing algorithm for constructing
paths to utilize that redundancy.
When network structure can be dictated
our results can be used to create scalable,
attack-tolerant infrastructures.
More generally, our results provide a theoretical formalism for evaluating the effects
of network structure on adversarial fault-tolerance.
\end{abstract}

@@

@@

While decentralized protocols have received much attention for their potential
fault tolerance applications,
centralized structures are always vulnerable to exploitation by non-technical means (i.e., coercion),
and there is a need for a better understanding of the relationship between network
structure and attack-tolerance.
We have proposed a network-based scheme for {\em adversarial} fault tolerance on the
butterfly topology,
utilizing a novel concurrent multipath routing algorithm.
We have also demonstrated how {\em partial trust transitivity},
in addition to being more realistic than infinite transitivity,
provides a theoretical foundation for
quantitative analysis of the relationship between trust,
network structure, and attack tolerance.

Such attacks include many forms of censorship and surveillance,
which have important social implications.
We have already discussed two such cases:
Pakistan's inadvertant censorship of YouTube
\cite{hunter_pakistan_2008}
and the FBI's surveillance-turned-censorship of Lavabit
\cite{poulsen_edward_2013}
The reader may wonder how our methods could be employed in scenarios
such as large-scale state-sponsored censorship.
Censorship-resistant infrastructure often replaces central servers
(e.g., the router in the 2008 YouTube incident) with multiple servers across
the world, synchronized through consensus protocols.
The {\em directory authorities} used by the Tor
\cite{dingledine_tor_2004} network are one example.
However, the size of such authority networks is often limited by the number of
trust relationships (degree) each node can maintain, and the inherent insecurity of
extending transitive trust to an ever-larger network.
Our work fills a much-needed gap by quantifying the connection between network-structure,
trust transitivity,
and attack-tolerance.
We provide both a theoretical framework and specific example of how network structure
can be engineered to leverage trust for a high level of attack-tolerance,
without sacrificing scalability.

@@

We have focused primarily on adversarial faults that block or
change messages (e.g., censorship).
Existing cryptographic techniques for circumventing surveillance
are relatively mature compared to those for tolerating censorship.
However, the techniques presented in this paper
are entirely compatible with, and in some cases could enhance, existing
anti-surveillance techniques.
For example, {\em man-in-the-middle} attacks exploit a privileged
network position to attack otherwise secure cryptography,
suggesting that structural approaches can complement cryptographic ones.

While our present proposal is specific to the butterfly topology,
the multipath fault tolerance scheme could
be applied to any network that has both sufficient redundancy and a
routing algorithm to discover independent paths.
For general networks, finding all such paths is NP-hard,
but efficient, suboptimal algorithms exist
\cite{reiter_resilient_1998}.
However, we have argued that attack-tolerance requires the ability to
influence network structure and reduce reilance on single points of failure.
Our work is most applicable to cases where the need for attack-tolerance
justifies investment in deliberate infrastructure.
For example, a coalition of groups supporting free expression could use our work
to construct a censorship-resistant communication network.
In general, such groups would need to invest resources into vetting their neighbors
to establish trust, but there are scenarios in which the attack-tolerance
requirement would justify that investment.
It is also worth noting that because faulty paths can be identified in our scheme,
it may at times be appropriate to assume mutual trust and revoke that relationship
when it is violated.
Any entities dependent on the proper functioning of the network would have an incentive
to resist attack in order to maintain their ability to participate.

@@

We have presented a novel concurrent multipath routing algorithm for the butterfly
topology,
as well as a scheme for using this algorithm to construct a highly attack-tolerant
virtual channel between any two nodes, even when no fully-trusted path exists
between them.
Under this scheme, the probability of an adversary causing an undetectable error
decreases exponentially with the network's effective redundancy.
The effective redundancy, in the case of the butterfly topology,
grows exponentially with the trust radius.
Furthermore, a small increase in the number of messages sent can compensate
for a large increase in the number of messages compromised by an adversary.
We have also demonstrated how the assumption of partial trust
transitivity can enable a quantitative analysis of the
relationships between network structure, trust, and attack-tolerance.
These results are directly applicable to systems in which the link
structure can be imposed by the designer,
and more generally, provide a theoretical foudnation that can be used more to evaluate
the role of network structure, trust transitivity, and effective redundancy
on attack-tolerance.
